A simplified Plackett-Luce likelihood function for rank orders

### 2024-04-03 inst/hankin-ejs.tex
rewording

In educational research, confidentiality of examination scores is
often an issue, and individual results are generally regarded as
sensitive and private information.  Nevertheless, it is common for a
student to possess some informative observations: the total enrollment
in a specific class and their individual ranking within that class;
table~\ref{educationtable} shows an apocryphal dataset.  What could a
student infer from such data?

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Supplementary Material, including data   %%
%% sets and code, should be provided in     %%
%% {supplement} environment with title      %%
%% and short description. It cannot be      %%
%% available exclusively as external link.  %%
%% All Supplementary Material must be       %%
%% available to the reader on Project       %%
%% Euclid with the published article.       %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{supplement}
\stitle{Very simplified likelihood}
\sdescription{A terse rmarkdown document that  recreates the figures and salient results of the submission}
\end{supplement}

>>>>

In educational research, confidentiality of examination scores is
often an issue, and individual results are generally regarded as
sensitive and private information.  Nevertheless, it is common for a
student to possess some informative observations, for example the
total enrollment in a specific class and their individual ranking
within that class.  Table~\ref{educationtable} shows an apocryphal
dataset: what could a student infer from such data?

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Supplementary Material, including data   %%
%% sets and code, should be provided in     %%
%% {supplement} environment with title      %%
%% and short description. It cannot be      %%
%% available exclusively as external link.  %%
%% All Supplementary Material must be       %%
%% available to the reader on Project       %%
%% Euclid with the published article.       %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{supplement}
  \stitle{R code source files}
  \sdescription{
    File {\tt hankin-ejs.Rmd} is a terse rmarkdown document that
    recreates the figures and salient results of the submission.
  }
\end{supplement}
